\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-12-04 exps.tex
updated some figs (pos)
Made it ugly

\begin{figure}[h!]
	\vspace{-10pt}
  \begin{SubFloat}{\label{delaycode:a}Original program}
    \centering
      \scriptsize
		\begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
emit TimerTriggered;
trap(T){
  abort(DoorOpened){
    await(TimeOut);
    exit(T); 
  }
}
\end{lstlisting}
  \end{SubFloat}
  \hspace{1cm}%
  \begin{SubFloat}{\label{delaycode:b}Program with delay constructs}
    \centering
		\begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
// No emit statement
trap(T){
  abort(DoorOpened){
    delay(10000 ms);
    exit(T);  
  }
}
\end{lstlisting}
	\end{SubFloat}
\caption{Replacing external timer with delay construct}
\label{delaycode}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot + [postaction={pattern=north east lines}] coordinates
                        {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot + [postaction={pattern=north west lines}] coordinates
                        {(Motor, 8.00) (AECS/CD2, 11.82)};
			\addplot + [postaction={pattern=dots}] coordinates
                        {(Motor, 6.42)};
			\addplot + [postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 7.53)};
			\addplot + [postaction={pattern=crosshatch}] coordinates
                        {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph2}
\end{figure}

>>>>

\begin{figure}[h!]
	\vspace{-10pt}
	\centering
  \begin{SubFloat}{\label{delaycode:a}Original program}
      \scriptsize
		\begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
emit TimerTriggered;
trap(T){
  abort(DoorOpened){
    await(TimeOut);
    exit(T); 
  }
}
\end{lstlisting}
  \end{SubFloat}
  \hspace{1cm}%
  \begin{SubFloat}{\label{delaycode:b}Program with delay constructs}
		\begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
// No emit statement
trap(T){
  abort(DoorOpened){
    delay(10000 ms);
    exit(T);  
  }
}
\end{lstlisting}
	\end{SubFloat}
\caption{Replacing external timer with delay construct}
\label{delaycode}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot + [fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot + [fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 8.00) (AECS/CD2, 11.82)};
			\addplot + [fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 6.42)};
			\addplot + [fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 7.53)};
			\addplot + [fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph2}
\end{figure}
